---
title: "Dynamic dashboard"
format:
  html:
    include-after-body: team-links-new-tab.html
---

```{r}
#| echo: false
# After deploying shiny_dashboard/ to shinyapps.io, set this to your live URL.
shiny_url <- "https://shokodera.shinyapps.io/ati-data-dashboard/"
deployed <- !grepl("YOUR_ACCOUNT", shiny_url, fixed = TRUE)
```

Explore ATI survey sites interactively: pick a metric, filter by habitat and shore, inspect the map and summary chart, then download the filtered table.

```{r}
#| echo: false
#| results: asis
if (deployed) {
  cat(sprintf(
    paste0(
      '<p><a class="btn btn-primary btn-lg" href="%s" target="_blank" rel="noopener">',
      "Open dynamic dashboard</a></p>\n",
      '<div class="ratio ratio-16x9 border rounded overflow-hidden mb-3">',
      '<iframe src="%s" title="ATI Dynamic Dashboard" ',
      'loading="lazy" style="border:0;width:100%%;height:100%%;min-height:720px;"></iframe>',
      "</div>\n",
      '<p class="text-muted small">If the embed is blank, ',
      '<a href="%s" target="_blank" rel="noopener">open the app in a new tab</a>.</p>\n'
    ),
    shiny_url, shiny_url, shiny_url
  ))
} else {
  cat(paste0(
    '<div class="callout callout-warning">\n',
    "<div class=\"callout-header\">Deploy required</div>\n",
    "<div class=\"callout-body\">\n",
    "<p>The Shiny app lives in <code>shiny_dashboard/</code> at the repo root. ",
    "Deploy it to shinyapps.io, then replace <code>YOUR_ACCOUNT</code> in ",
    "<code>Dynamic_dashboard.qmd</code> with your account name and re-render this site.</p>\n",
    "<p>Local preview:</p>\n",
    "<pre><code>shiny::runApp(\"shiny_dashboard\")</code></pre>\n",
    "<p>Full steps: <code>shiny_dashboard/README.md</code>.</p>\n",
    "</div></div>\n"
  ))
}
```

## What you can do

-   Switch among habitat, distance, Turbinaria %N, bleaching, mortality, benthic cover, eDNA richness, temperature, and acoustic metrics
-   Filter master ATI sites by habitat, island shore, and distance from shore
-   Click markers for site details; download the filtered CSV

Temperature and acoustic layers use their own monitoring networks (different site IDs), so habitat/shore/distance filters apply to the ATI master sites only.
